\documentclass{beamer}

    \title[Ordenacao Distribuida] % (optional, only for long titles)
    {Ordenacao Distribuida de Eventos}
    \subtitle{Algoritmo de Lamport e Totally Ordered Multicast}
    \author[Melo] % (optional, for multiple authors)
    {R. D.~Melo\inst{1}}
    \institute[Universidade Federal do Rio de Janeiro (UFRJ)] % (optional)
    {
    \inst{1}%
    Departamento de Engenharia de Computacao e Informacao\\
    ECI/UFRJ
    }
    \date[2018] % (optional)
    {COS470 Sistemas Distribuidos, 2018}
    \subject{Computer Science}

    \newcommand{\code}[1]{\texttt{#1}}

    \AtBeginSection[] {
        \begin{frame}
            \frametitle{Table of Contents}
            \tableofcontents[currentsection]
        \end{frame}
    }

    \begin{document}
        \frame{\titlepage}
        \begin{frame}
            \frametitle{Sumario}
            \tableofcontents[currentsection]
            %Content goes here
        \end{frame}
        \begin{frame}
            \frametitle{This is the second slide}
            \framesubtitle{A bit more information about this}
            %More content goes here
        \end{frame}
        % etc

        \begin{frame}[allowframebreaks]
            \frametitle<presentation>{Referencias Bibliograficas}
            \begin{thebibliography}{10}

                \beamertemplateonlinebibitems
                \bibitem{Shin2014}
                D.~Shin.
                \newblock {\em Reliable Multicast Chat}.
                \newblock University of California - Irvine.
                \newblock https://github.com/daeyun/reliable-multicast-chat, 2014.

                \beamertemplateonlinebibitems
                \bibitem{Tyrväinen2016}
                J.~Tyrväinen.
                \newblock {\em Concurrent solution for lamport clocks}.
                \newblock https://github.com/religiosa/lamportClocks, 2016.

                \beamertemplateonlinebibitems
                \bibitem{Wolff2014}
                C.~Wolff.
                \newblock Microsoft/NY.
                \newblock {\em Distributed Systems}.
                \newblock https://github.com/c-w/ug4\_DistributedSystems, 2014.

                \beamertemplateonlinebibitems
                \bibitem{Whittaker2015}
                J.~Whittaker.
                \newblock {\em An implementation of Lamport timestamps}.
                \newblock https://github.com/mwhittaker/clocks, 2015.

                \beamertemplateonlinebibitems
                \bibitem{Kiehl2015}
                C.~Kiehl.
                \newblock Amazon/WA.
                \newblock {\em Parallelism in one line}.
                \newblock https://wiki.python.org/moin/TcpCommunication, 2012.

                \beamertemplateonlinebibitems
                \bibitem{Fortuner2017}
                B.~Fortuner.
                \newblock Amazon/WA.
                \newblock {\em Intro to Threads and Processes in Python}.
                \newblock https://medium.com/@bfortuner/python-multithreading-vs-multiprocessing-73072ce5600b, 2017.

                \beamertemplateonlinebibitems
                \bibitem{McMillan2018}
                Gordon.~McMillan.
                \newblock Official 3.5.2 documentation.
                \newblock {\em Socket Programming }.
                \newblock https://docs.python.org/3/howto/sockets.html, 2017.

                \beamertemplateonlinebibitems
                \bibitem{Python2017}
                Python Software Foundation.
                \newblock Official 3.5.2 documentation.
                \newblock \code{multiprocessing}:{\em Process-based parallelism}.
                \newblock https://docs.python.org/3.5/library/multiprocessing.html, 2018.

            \end{thebibliography}
          \end{frame}
    \end{document}
